Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-09-22 manuscript/Chapter3-manuscript.Rmd
update methods

*Dead by Daylight* is a survival horror asymmetric multiplayer online game developed by the videogame company Behavior Interactive Inc. In this game, players get to chose if they wish to play has a predator or a prey. The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment. The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through an exit door and win the match. Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g. bolder vs cautious prey, or ambush vs roaming predator). During our study period, the game offered X playable predator avatars, and X prey avatars. The virtual environment where matches take place is composed of fixed and procedurally generated items (e.g. vegetation, mazes, buildings) that constitute its structure. Some of these environments are larger than others, with varying levels or buildings. However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a feature where predators have visual cues on the generators [@FraserFranco.etal2022].

>>>>

*Dead by Daylight* is a survival horror asymmetric multiplayer online game developed by Behavior Interactive Inc. In this game, players get to chose if they wish to play has a predator or a prey. The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment. The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through one of two exit doors and win the match. Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g. bolder vs cautious prey, or ambush vs roaming predator). During our study period, the game offered 23 playable predator avatars. The virtual environment where matches take place is composed of fixed and procedurally generated items (e.g. vegetation, mazes, buildings) that constitute its structure. Some of these environments are larger than others, with varying levels or buildings. However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a feature where predators have visual cues on the generators [@FraserFranco.etal2022]. There were 35 virtual game environments available for play during our study period.
